### 2018-04-30 paper/intro.tex
up

In this paper, we demonstrate how good performance can be reconciled with strong privacy protection in data-sharing systems. We present \name{}, a novel fully decentralized, autonomous,
% approach that provides a 
and self-organizing file sharing service between the \squad{}s of different users that preserves user privacy
in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file
transfers. Close distance among users enable them to share
routing information out-of-band, e.g. from their
\squad. In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
do not keep it available for anyone else in the future. \emph{Second}, we
rely on distributed machine learning techniques to predict the future
availability of user devices, and use this ability to implement a \emph{probabilistic predictive onion routing} mechanism. The predictive nature of our routing allows us to overcome the inherent fragility of pure P2P data-sharing schemes.

@@

Our contributions are as follows: \david{please update}
\begin{itemize}
\item We showed the effectiveness of \iac{ANOBE} scheme by \textcite{ANOBE} 
  to build a \ac{DeBE} as required by \name to
  provide.... 
\item A \squad overlay 
\item Model the user’s behavior as a Hidden Markov Models (HMMs)
\item SPOR provides stateless algorithms for the onion-routing.
\item An evaluation testbed where each user’s behavior
\end{itemize}

In the following, we detail \name 's concepts and approach...

% Cashmere: resilient anonymous routing.
% Route fingerprinting in anonymous communications.
% Bridging and fingerprinting:
% Epistemic attacks on route selection
% Breaking the collusion detection mechanism of morphmix
% Denial of service or denial of security? How attacks
% on reliability can compromise anonymity

>>>>

In this paper, we demonstrate how good performance can be reconciled
with strong privacy protection in data-sharing systems. We present
\name{}, a novel fully decentralized, autonomous,

% approach that provides a 
and self-organizing file sharing service between the \squad{}s of different users that preserves user privacy
in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file
transfers. Close distance among users enable them to share
routing information out-of-band, e.g. from their
\squad. In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
do not keep it available for anyone else in the future. \emph{Second}, we
rely on distributed machine learning techniques to predict the future
availability of user devices, and use this ability to implement a \emph{probabilistic predictive onion routing} mechanism. The predictive nature of our routing allows us to overcome the inherent fragility of pure P2P data-sharing schemes.

@@

Our contributions are as follows: 
\begin{itemize}
\item We have designed \name, a novel fully decentralized, autonomous,
and self-organizing file sharing service among users based on a novel
concept named Probabilistic Onion Routes (POR), which combines onion routing with
probabilistic node selection, informed by random peer sampling and
Hidden Markov Model predictions for node availability. 
\item  We have demonstrated the successfulness of our approach. Even
  suboptimal prediction results in successful file transfer with high
  probability. 
\end{itemize}

In the following, in Section~\ref{system-model}, we introduce the
adversary model the desired privacy properties of \name. Section~\ref{design}
introduce the design of our proposed solution. Section~\ref{Performance}
evaluates the proposed approach. In Section~\ref{security-discussion}, we lead a security discussion
about advantages, shortcomings of our approach.
Finally, Section~\ref{conclusion} discusses future work and conclusions.
% Cashmere: resilient anonymous routing.
% Route fingerprinting in anonymous communications.
% Bridging and fingerprinting:
% Epistemic attacks on route selection
% Breaking the collusion detection mechanism of morphmix
% Denial of service or denial of security? How attacks
% on reliability can compromise anonymity

### 2018-04-30 paper/system-model.tex
up

\paragraph*{In the cloud setting} if Alice wants to share a file with
Bob, she picks up and pushes one of her files, from one of her devices, to the cloud
provider, to make it available to Bob that will thereafter get it from
one of its devices. The use of the cloud provider as a third party
provides two main privacy properties, which we have to consider when
changing the setting to that of \ac{P2P}~\cite{DevilInMetadata}:
\begin{itemize}
\item Alice and Bob are the only ones who learn 
about Alice sharing a file with Bob, except for the cloud provider.
\item Alice and Bob learn nothing about each others' devices, \ie 
they cannot map any device as belonging to each other, except for the
cloud provider that learn it.
\end{itemize}

>>>>

\paragraph*{In the cloud setting} if Alice wants to share a file with
Bob, she picks up and pushes one of her files, from one of her devices, to the cloud
provider, to make it available to Bob that will thereafter get it from
one of its devices. The use of the cloud provider, as a third party,
provides two main privacy properties, which we have to consider when
changing the setting to that of \ac{P2P}~\cite{DevilInMetadata}:
\begin{itemize}
\item Alice and Bob are the only ones who learn 
about Alice sharing a file with Bob, except for the cloud provider.
\item Alice and Bob learn nothing about each others' devices, \ie 
they cannot map any device as belonging to each other, except for the
cloud provider that learn it.
\end{itemize}
